\documentclass{letter}
\usepackage{hyperref}
\signature{Nam}
\begin{document}

\begin{letter}{}
\opening{Dear Diary,}


It has been a fruitful academic year with many new challenges. I have learnt a lot in the LANG1003I course. In particular, I gained some new skills that I did not expect to know through completing the multimodal group project.

 
First of all, I learnt quite a lot of video editing skills through this project. My groupmates introduced me to a software called "Animaker," which is amazing for video editing beginners like myself, who had no experience in this field. With its built-in tutorials, I quickly became familiar with video editing, which enabled me to learn these skills effectively. I think this will be a very useful competency for my future learning experience. Since I am an engineering student, I need to have good working ability with different technologies. This is a fantastic opportunity for me to expose myself to the field of video editing.
 
Moreover, I enhanced my spoken language via this project. I know that I am lacking English language skills, so I was quite nervous about doing this project. This assignment required me to record a voice-over track to insert into the video. To ensure I delivered quality work, I encouraged myself to write a script for the voice-over track and practiced a few times beforehand. I gained confidence and improved in my English language skills with the constant effort that I put in. Through peer evaluation within my group, I knew my weaknesses in spoken English, and I improved a lot with the valuable suggestions that were provided by my groupmates. Now, I am less intimidated by English-related work.
 
To conclude, I acquired video editing skills and improved my English competency. I am thankful to my peers who taught me many more skills that are not covered in this diary. I have had a wonderful learning experience.
 

\closing{Yours sincerely,}



\end{letter}
\end{document}